% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

% include the `tex` instructions that takes care of loading packages and defining commands
\include{resume-commands}



\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

\maintitle{Seb Insua}{Product Hacker}  % title on top of the document

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{http://github.com/sebinsua}{github.com/sebinsua}\sbull
\href{http://sebinsua.com}{sebinsua.com}\sbull
\href{https://news.ycombinator.com/user?id=lhnz}{news.yc/sebinsua}\sbull
\href{http://twitter.com/sebinsua}{twitter.com/sebinsua}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Engineer with a passion for product design, deep interest in the humanities and an entrepreneurial mindset.}
\\
\\
I was sixteen when my fascination with technology picked up steam. My interest was piqued on discovering a small homebrew community for the handheld gaming device, the GP32. It was inspiring to see a flourishing community of hobbyists creating games for each other and I still maintain that we learn best through play.\newline

I'm product-focused and passionate about making an impact in the world. I've always got side projects on-the-go, from the non-profit online music zine that I bootstrapped to 15 regular contributors to the defunct travel startup that I taught myself Objective-C with.\newline

My speciality is in combining technical knowledge with lateral thinking. I am fascinated by interdisciplinary thinking and due to this appreciate being part of true cross-functional teams. Techwise I have a full-stack skillset but recently have worked mainly in JavaScript, Node.JS, and Swift. I favour technology philosophies from: \href{http://12factor.net}{the twelve-factor app}, functional programming, micro-services, behaviour-driven development (\acr{BDD}) and \href{http://infoq.com/presentations/Simple-Made-Easy}{Simple Made Easy}.\newline

\end{multicols}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical specialties:}
  {Full-stack software design and implementation. I love to work on on the back-end creating \acr{REST}ful \acr{API}s using Node.JS; but also work with mobile technologies like Swift and Cocoa Touch, and on the front-end using JavaScript, AngularJS, \acr{HTML5} and \acr{CSS3}. I follow the mantra \emph{the right tool for the right job} and quickly pick things up.}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Leadership, Product \& Operations:}
  {Experience in team leadership (lead teams of 5+ people); product/technical mentor for Seedcamp companies; multi-faceted approach to product creation: customer development, UX, business modelling, development; ran a Hackathon with 80 participants, etc.}

\spacedhrule{1.5em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.momentumlabs.io}{Momentum Labs}}
  {\textsc{London, United Kingdom}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {Founder of Spokes}
    {Sep \apo14 -- Present}
    {\bodytext{\emph{An professional networking iOS app to connect locals with complementary skills for coffee.}
    \begin{itemize}[leftmargin=0cm]
      \item \href{https://marvelapp.com/174c9e}{The UI and UX were designed using Sketch.}
      \item The back-end API was architected and developed using Node.js, Koa.js, the graph database Neo4j and Redis.
      \item The front-end app is nearing completion and was built using Swift, Cocoa Touch, ReactiveCocoa, and a few other Cocoapods.
      \item I'm currently testing it with early adopters and hope to launch sometime in 2015.
    \end{itemize}
  }}

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {Freelancer}
    {Jun \apo13 -- Present}
    {\bodytext{\emph{Freelancing, consulting and open-source activities.}
    \begin{itemize}[leftmargin=0cm]
      \item During crunchtime at a London startup I sacrificed my freetime to help them work on a Phonegap game in which you try to predict the results of future Football games. I finish my normal job at 5:30PM and I run over there to work an extra 5 hours before going home.
      \item \href{https://github.com/sebinsua/express-keenio}{An Express.js middleware to allow one-line installation of analytics into Node.JS projects} for the \href{https://www.sequoiacap.com/}{Sequoia Capital} backed Silicon Valley startup \href{http://keen.io}{Keen IO}. This was a project born out of an idea I suggested as a way of reducing the time-to-setup of their analytics service from multiple hours/days to around 15 seconds.
      \item A one-week integration of analytics into \href{http://crowdsurge.com}{CrowdSurge's stores} to help visualise user flows with funnels, segmentation, etc.
      \item A work-in-progress JavaScript object transformation library/philosophy called \href{https://github.com/sebinsua/jstruct}{Jstruct}.
      \item Sporadic articles on user experience, group psychology, technology and philosophy.
    \end{itemize}
  }}
}

\headedsection
  {\href{http://gov.uk/government/organisations/home-office}{Home Office}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Contract Node.JS Specialist}
    {Jan \apo15 -- Present}
    {\bodytext{\emph{The Home Office is a ministerial department of the Government of the United Kingdom, responsible for immigration, security, and law and order.}
    }}
}

\headedsection
  {\href{http://www.red-badger.co.uk}{Red Badger}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Contract Node.JS Consultant}
    {Mar \apo14 -- Jul \apo14}
    {\bodytext{\emph{Red Badger is a creative software workshop.}
    \begin{itemize}[leftmargin=0cm]
      \item This was a client-facing role in which I provided training so that key knowledge of a system could be passed from an internal team to an external team.
      \item I worked on features and fixes with technologies including CoffeeScript, Node.JS, RabbitMQ, Elasticsearch and Redis.
    \end{itemize}
    }}
}

\headedsection
  {\href{http://www.hailocab.com}{Hailo}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Contract JavaScript Engineer}
    {Sep \apo13 -- Jan \apo14}
    {\bodytext{\emph{Hailo is the evolution of the hail -- a free smartphone app which puts people just two taps away from a licensed taxi, and lets cabbies get more passengers when they want them.}
    \begin{itemize}[leftmargin=0cm]
      \item Created a series of single-page dashboard apps. Conversations with internal customers helped me to come up with ideas on how to simplify business processes. For example a way of signing off groups of driver's profile changes was given a UX that defaulted to approval but forced the user to sign a receipt of the changes: this helps with speed while also ensuring accountability.
      \item Other components were created so that behaviour relating to presentation was well-separated from configuration and data input; or made so that they could be updated in real-time, for example: an animated map of driver locations.
      \item The SOA lacked some orchestration features so building pages sometimes required a lot of HTTP requests. Therefore to simplify this we made a lot of use of the promise library Q.js as well as underscore.js to filter and aggregate responses.
    \end{itemize}
    }}
}

\headedsection
  {\href{http://www.bizzby.com}{BIZZBY}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Senior Node.JS Developer}
    {Apr \apo13 -- Jun \apo13}
    {\bodytext{\emph{Bizzby is app your service to help you book a trusted local service in 30 seconds.}
    \begin{itemize}[leftmargin=0cm]
      \item Various APIs and CMS features.
    \end{itemize}
  }}
}

\headedsection
  {\href{http://www.werinteractive.com}{We R Interactive}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Lead Node.JS Developer}
    {Oct \apo12 -- Apr \apo13}
    {\bodytext{
        \emph{We R Interactive blends the best of games, film and TV production to create social games that bring global audiences together around sport and music.}
        \begin{itemize}[leftmargin=0cm]
            \item Designed and lead the creation of a back-end system to support a sport game as well as recruiting developers for my team.
            \item The system was decomposed into multiple services and stored data in Cassandra. I created a service which would automatically generate a series of questions from a stream of data and a template, a real-time market-outcome resolution service that would automatically resolve a series of previously generated questions depending on a simple DSL and a stream of real-life data, and a service that could have data pushed to or pulled from it and parse this data into a common format before feeding it into a message queue for deeper processing. I also helped direct my team in prototyping an early \acr{REST}ful front-end API and Phonegap version of the game.
            \item Setup a continuous integration system using Jenkins, and used Puppet to automate deployment of some of the services to AWS. Later on third-party data issues were reported to stakeholders and dealt with through design chances relating to logging and testing the data quality.
        \end{itemize}
    }}
}

\headedsection
  {\href{http://www.saffrondigital.com}{Saffron Digital}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Lead Python Developer}
    {Oct \apo10 -- Oct \apo12}
    {\bodytext{
  \emph{Saffron Digital is the global, market-leading provider of connected device video, DRM, advertising and platform services. Saffron Digital was acquired by HTC in 2011.}
  \begin{itemize}[leftmargin=0cm]
      \item Project leader and architect of the HTC Watch project in which I lead a team of five developers. Due to my early work on internationalisation and implementation of multiple payment services we were able to run this globally in close to 20 countries. Later on the project became a baseline for future web services for other clients.
      \item Significant input in re-engineering development process as we moved from being a startup to a larger company. For example: an engineer empowering company culture; Git instead of SVN; continuous integration; modern deployment tools; etc.
      \item Architecture and development of a new platform based on understandings gleaned from previous services. Worked on service to orchestrate and configure encoders in order to run encodes in parallel on AWS.
      \item A client-side application for Samsung Connected TVs and set-top boxes written in object-orientated JavaScript.
  \end{itemize}}
  }
  \headedsubsection
    {PHP Developer}
    {Feb \apo10 -- Oct \apo10}
    {\bodytext{
  \begin{itemize}[leftmargin=0cm]
      \item A RESTful web service for FOX to support a fully localised Family Guy video streaming Android application. A CMS was also created as well as reporting tools to give the business metrics to measure activity.
      \item A web service for Paramount Studio’s the League of Extraordinary Dancers iPhone Application. This was interoperable with the iTunes video store in order to check receipts.
  \end{itemize}
    }}
}

\begin{center}
  \emph{Please refer to \href{http://www.linkedin.com/in/heyseb}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {University of Kent}
  {\textsc{Canterbury, United Kingdom}} {%
  \headedsubsection
    {Bachelor's degree in Computer Science}
    {2005 -- 2009}
    {\bodytext{Courses included Computer Systems and Algorithms, Data Structures and Complexity, Data Mining and Knowledge Discovery, Operating Systems and Architecture, Software Engineering Practice, Database Systems, and Distributed Systems and Networks. While studying here I also coordinated and guided a team of four developers creating a DJ mixing application in Java for my final project.}
  }
}

\headedsection
  {Cranbrook School}
  {\textsc{Cranbrook, United Kingdom}} {%
  \headedsubsection
    {GCSEs \& A-Levels \textnormal{(secondary education)}}
    {2000 -- 2005}
    {\bodytext{}
  }
}

\spacedhrule{0em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {}
  {Anthropology, antifragility, economics, sociology, philosophy, poetry, product design, startups and user experience.}

\end{document}
